### 2009-05-14 doc/tutorials/ws-programming-tutorial/doc/tex_appendix/appendix.tex
Reorganizing doc catalogue and enabling make doc
Added a modified doc folder refering to the new folder structure of the examples

In order to learn more about ARC several other tutorials and documentations have been written:
\begin{itemize}
 \item ARC Web Services Quick Usage Guide~\cite{2008_UNKNOWN}
 \item The Hosting Environment of the Advanced Resource Connector middleware~\cite{2008_Cameron}.
 \item Security framework of ARC1~\cite{QIANG_2008}.
 \item Documentation of the ARC storage system~\cite{Nagy_2008}.

@@

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:mcc.xsd,
	caption={[XML schema of configuration files.]\textbf{XML schema of configuration files.}}
	]{../../../src/hed/libs/loader/mcc.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:tcp.xsd,
	caption={[XML schema of the TCP component.]\textbf{XML schema of the TCP component.}}
	]{../../../src/hed/mcc/tcp/tcp.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:tls.xssd,
	caption={[XML schema of the TLS component.]\textbf{XML schema of  the TLS component.}}
	]{../../../src/hed/mcc/tls/tls.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:http_xsd,
	caption={[XML schema of the HTTP component.]\textbf{XML schema of the HTTP component.}}
	]{../../../src/hed/mcc/http/http.xsd}

>>>>

In order to learn more about ARC several other tutorials and documentations have been written:
\begin{itemize}
 \item ARC Web Services Quick Usage Guide~\cite{2008_UNKNOWN}
 \item The Hosting Environment of the Advanced Resource Connector middleware~\cite{2008_Cameron}.
 \item Security framework of ARC1~\cite{QIANG_2008}.
 \item Documentation of the ARC storage system~\cite{Nagy_2008}.
 \item Eclipse WTP 1.5.1, Introduction to the WSDL Editor, \url{http://wiki.eclipse.org/index.php/Introduction_to_the_WSDL_Editor}

@@

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:mcc.xsd,
	caption={[XML schema of configuration files.]\textbf{XML schema of configuration files.}}
	]{../../../../src/hed/libs/loader/mcc.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:tcp.xsd,
	caption={[XML schema of the TCP component.]\textbf{XML schema of the TCP component.}}
	]{../../../../src/hed/mcc/tcp/tcp.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:tls.xssd,
	caption={[XML schema of the TLS component.]\textbf{XML schema of  the TLS component.}}
	]{../../../../src/hed/mcc/tls/tls.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:http_xsd,
	caption={[XML schema of the HTTP component.]\textbf{XML schema of the HTTP component.}}
	]{../../../../src/hed/mcc/http/http.xsd}

### 2009-05-14 doc/tutorials/ws-programming-tutorial/doc/tex_echoservice/echoservice.tex
Added a modified doc folder refering to the new folder structure of the examples

The WSDL file that specifies the here presented Echo Web Service is shown in
Listing~\ref{lst:echo_wsdl}.
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:echo_wsdl,
	caption={[WSDL file describing the echo service. Filename: echo.wsdl]
	\textbf{WSDL file describing the echo service. Filename: echo.wsdl}}
	]
{../src/services/echoservice/echo.wsdl}
\task{TODO: Validate the WSDL Listing}

@@

\lstsetCPP
\lstinputlisting
	[
	label=lst:echo_service_cpp,
	caption={[Implementation of the Echo Web Service.]
	\textbf{Implementation of the Echo Web Service.}}
	]
{../src/services/echoservice/echoservice.cpp}

@@

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:echo_hed_configuration_xml, float=htb,
	caption={[Server configuration file of the Echo Web Service]
	\textbf{Server configuration file of the Echo Web Service}}
	]
{../src/services/echoservice/arched_echoservice.xml}

@@

\lstsetCPP
\lstinputlisting
	[
	label=lst:client_echo_cpp,
	caption={[Implementation of the client program.]
	\textbf{Implementation of the client program.}}
	]
{../src/clients/echoclient/echoclient.cpp}

>>>>

The WSDL file that specifies the here presented Echo Web Service is shown in
Listing~\ref{lst:echo_wsdl}.
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:echo_wsdl,
	caption={[WSDL file describing the echo service. Filename: echo.wsdl]
	\textbf{WSDL file describing the echo service. Filename: echo.wsdl}}
	]
{../examples/src/services/echoservice/echo.wsdl}
\task{TODO: Validate the WSDL Listing}

@@

\lstsetCPP
\lstinputlisting
	[
	label=lst:echo_service_cpp,
	caption={[Implementation of the Echo Web Service.]
	\textbf{Implementation of the Echo Web Service.}}
	]
{../examples/src/services/echoservice/echoservice.cpp}

@@

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:echo_hed_configuration_xml, float=htb,
	caption={[Server configuration file of the Echo Web Service]
	\textbf{Server configuration file of the Echo Web Service}}
	]
{../examples/src/services/echoservice/arched_echoservice.xml}

@@

\lstsetCPP
\lstinputlisting
	[
	label=lst:client_echo_cpp,
	caption={[Implementation of the client program.]
	\textbf{Implementation of the client program.}}
	]
{../examples/src/clients/echoclient/echoclient.cpp}

### 2009-05-14 doc/tutorials/ws-programming-tutorial/doc/tex_timeservice/timeservice.tex
Added a modified doc folder refering to the new folder structure of the examples

In ARC, the services are implementated as plugins such that they can easily be included or excluded by modifiying the server configuration file as it was seen in Listing~\ref{lst:arched_arcecho_xml}.
The class needed to be implemented for the Web Service inherits from the class \textit{Service}, which itself is defined in the ARC library. The proper class definition of the object \textit{TimeService} is defined in the corresponding header as shown in Listing~\ref{lst:time_arched_h}.
\lstsetCPP%
\lstinputlisting[
	label=lst:time_arched_h,
	caption={[Header file of the Time Web Service.]
	\textbf{Header file of the Time Web Service.}}
	]%
{../src/services/timeservice/timeservice.h}%
The class \textit{Service} renders the possibility to implement the method \textit{process}.
Listing~\ref{lst:time_arched_cpp} contains the C++ implementation of the Time Web Service plugin.
The key element for each plugin is the struct \textit{PluginDescriptor} named \textit{PLUGINS\_TABLE\_NAME} to be seen in line~\ref{lst_code:time_cpp_ptn}. 
%The struct defines basic entities of the service and provides a pointer to the method which is able to create an instance of the time service plugin.
Within the struct, a unique plugin name, the type of the plugin, its version and a pointer to a function which returns the instance of the time service has to be defined.
The function which returns the pointer of the instance is desclared in line~\ref{lst_code:time_cpp_get_service}. 
Within the interface an object \textit{PluginArgument} is demanded as a parameter. 
But since the plugin that is now written inherits from the class \textit{Service}, one can expect the \textit{PluginArgument} to be of a special subclass \textit{ServicePluginArgument}.
%	In the first line of the service the object is downcasted with the operator dynamic_cast
The \textit{ServicePluginArgument} provides access to the server configuration and to the message chain of the service which later may be useful.\\

@@

%
%
% \textcolor{white}{newline}
\lstsetCPP%
\lstinputlisting[
	label=lst:time_arched_cpp,
	caption={[Implementation of the Time Web Service.]
	\textbf{Implementation of the Time Web Service.}}
	]%
{../src/services/timeservice/timeservice.cpp}%

@@

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:time_arched_xml,float=htb,
	caption={[Configuration for the Time Web Service.]
	\textbf{Configuration for the Time Web Service.}}
	]
{../src/services/timeservice/arched_timeservice.xml}

@@

The source code of the client can be inspected in Listing~\ref{lst:time_client_cpp} and consists basically of one main function.
Within the line~\ref{lst_code:time_client_cpp_logger} the object \textit{Logger} is initialized.
Due to the configuration of the the \textit{Logger} in the following lines, the messages passed to it will be redirected to the standard error stream.  For the components of the protocol stack, which  are likewise loaded dynamically, one needs to specify the installation directory of ARC in line~\ref{lst_code:time_client_cpp_init}.\\
%\textcolor{white}{newline}
\lstsetCPP
\lstinputlisting
	[
	label=lst:time_client_cpp,
	caption={[Souce code of the client program.]
	\textbf{Souce code of the client program}}
	]
{../src/clients/timeclient/timeclient.cpp}

>>>>

In ARC, the services are implementated as plugins such that they can easily be included or excluded by modifiying the server configuration file as it was seen in Listing~\ref{lst:arched_arcecho_xml}.
The class needed to be implemented for the Web Service inherits from the class \textit{Service}, which itself is defined in the ARC library. The proper class definition of the object \textit{TimeService} is defined in the corresponding header as shown in Listing~\ref{lst:time_arched_h}.
\lstsetCPP%
\lstinputlisting[
	label=lst:time_arched_h,
	caption={[Header file of the Time Web Service.]
	\textbf{Header file of the Time Web Service.}}
	]%
{../examples/src/services/timeservice/timeservice.h}%
The class \textit{Service} renders the possibility to implement the method \textit{process}.
Listing~\ref{lst:time_arched_cpp} contains the C++ implementation of the Time Web Service plugin.
The key element for each plugin is the struct \textit{PluginDescriptor} named \textit{PLUGINS\_TABLE\_NAME} to be seen in line~\ref{lst_code:time_cpp_ptn}. 
%The struct defines basic entities of the service and provides a pointer to the method which is able to create an instance of the time service plugin.
Within the struct, a unique plugin name, the type of the plugin, its version and a pointer to a function which returns the instance of the time service has to be defined.
The function which returns the pointer of the instance is desclared in line~\ref{lst_code:time_cpp_get_service}. 
Within the interface an object \textit{PluginArgument} is demanded as a parameter. 
But since the plugin that is now written inherits from the class \textit{Service}, one can expect the \textit{PluginArgument} to be of a special subclass \textit{ServicePluginArgument}.
%	In the first line of the service the object is downcasted with the operator dynamic_cast
The \textit{ServicePluginArgument} provides access to the server configuration and to the message chain of the service which later may be useful.\\

@@

%
%
% \textcolor{white}{newline}
\lstsetCPP%
\lstinputlisting[
	label=lst:time_arched_cpp,
	caption={[Implementation of the Time Web Service.]
	\textbf{Implementation of the Time Web Service.}}
	]%
{../examples/src/services/timeservice/timeservice.cpp}%

@@

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:time_arched_xml,float=htb,
	caption={[Configuration for the Time Web Service.]
	\textbf{Configuration for the Time Web Service.}}
	]
{../examples/src/services/timeservice/arched_timeservice.xml}

@@

The source code of the client can be inspected in Listing~\ref{lst:time_client_cpp} and consists basically of one main function.
Within the line~\ref{lst_code:time_client_cpp_logger} the object \textit{Logger} is initialized.
Due to the configuration of the the \textit{Logger} in the following lines, the messages passed to it will be redirected to the standard error stream.  For the components of the protocol stack, which  are likewise loaded dynamically, one needs to specify the installation directory of ARC in line~\ref{lst_code:time_client_cpp_init}.\\
%\textcolor{white}{newline}
\lstsetCPP
\lstinputlisting
	[
	label=lst:time_client_cpp,
	caption={[Souce code of the client program.]
	\textbf{Souce code of the client program}}
	]
{../examples/src/clients/timeclient/timeclient.cpp}

### 2009-05-14 doc/tutorials/ws-programming-tutorial/doc/tex_tls_echoservice/tls_echoservice.tex
Added a modified doc folder refering to the new folder structure of the examples

The TLS Echo Web Service implementation is almost the same as the one presented in the previous chapter. Merely the Class name and the namespace of the service have been changed. The only modification is done within the server configuration file which is displayed in Listing~\ref{lst:tls_echo_arched_xml}.
\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:tls_echo_arched_xml,float=htb,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/tlsechoservice/arched_tls_echoservice.xml}
The first change is in line~\ref{lst_code:tls_echo_arched_xml_plugin}. As to be seen, another plugin called \textit{mcctls} will be loaded by the \textit{ModuleManager}. The second change is the new element which has been placed between the TCP and the HTTP component, see line~\ref{lst_code:tls_echo_arched_xml_component}. Within the TLS element the certificates can be declared using the elements \textit{KeyPath}, \textit{CertificatePath}, \textit{CACertificatePath} and \textit{CACertificatesDir}.
% \begin{verbatim}
% <KeyPath>./clientKey.pem</KeyPath>
% 
% <CertificatePath>./clientCert.pem</CertificatePath>
% 
% <CACertificatePath>./serviceCA.pem</CACertificatePath>
% 
% <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
% \end{verbatim}
% or
% \begin{verbatim}
% <ClientSSLConfig FromFile='filename'/>
% \end{verbatim}
% \task{You can put the ClientSSLConfig into a separate file, then use <ClientSSLConfig FromFile='filename'/> in each service, and then you don't need to change everywhere - proposed by Zsombor - but I can't find any example *hrmlgrmpf*...}

%\lstsetCPP
%\lstinputlisting
%	[
%	label=lst:tls_echo_service_cpp,
%	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
%	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
%	]
%{../src/services/tlsechoservice/tlsechoservice.cpp}
%
% Lassen wir mal weg....
%
%
% \lstsetKSH
% \begin{lstlisting}[
% label=lst:tls_echo_arched_invoke,float=htb,
% caption={[Transformation in eine uniforme konzentrische Verteilung.]
%          \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
% $ rm -f /var/log/arched.log
% $ arched -c arched_echoservice.xml  && echo jo ||echo n
% $ tail -n100 -f /var/log/arched.log
% $ killall arched
% \end{lstlisting}
% 
%        ...das auch.....

@@

In this section a new way to implement the client will be introduced. As already mentioned in section~\ref{sec:timeservice_client}, the protocol stack of the client is built up in almost the same way as the one of the service. Indeed, the class~\textit{ClientSOAP} composes the stack with the same MCCs used for the service. Once this is known, it is self-evident to create the client in a simlar manner like the service with an own configuration file.
Listing~\ref{lst:tls_echo_client_cpp} shows the source code of the client program. The main difference to the simple Echo Client presented in the previous chapter is that now the information about the client protocol stack is encapsulated within a configuration file.\\
\lstsetCPP
\lstinputlisting
	[
	label=lst:tls_echo_client_cpp,
	caption={[Client programm which is capable to load a configuration file]
	\textbf{Client programm which is capable to load a configuration file}}
	]
{../src/clients/tlsechoclient/tlsechoclient.cpp}

>>>>

The TLS Echo Web Service implementation is almost the same as the one presented in the previous chapter. Merely the Class name and the namespace of the service have been changed. The only modification is done within the server configuration file which is displayed in Listing~\ref{lst:tls_echo_arched_xml}.
\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:tls_echo_arched_xml,float=htb,
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../examples/src/services/tlsechoservice/arched_tls_echoservice.xml}
The first change is in line~\ref{lst_code:tls_echo_arched_xml_plugin}. As to be seen, another plugin called \textit{mcctls} will be loaded by the \textit{ModuleManager}. The second change is the new element which has been placed between the TCP and the HTTP component, see line~\ref{lst_code:tls_echo_arched_xml_component}. Within the TLS element the certificates can be declared using the elements \textit{KeyPath}, \textit{CertificatePath}, \textit{CACertificatePath} and \textit{CACertificatesDir}.
% \begin{verbatim}
% <KeyPath>./clientKey.pem</KeyPath>
% 
% <CertificatePath>./clientCert.pem</CertificatePath>
% 
% <CACertificatePath>./serviceCA.pem</CACertificatePath>
% 
% <CACertificatesDir>/etc/grid-security/certificates</CACertificatesDir>
% \end{verbatim}
% or
% \begin{verbatim}
% <ClientSSLConfig FromFile='filename'/>
% \end{verbatim}
% \task{You can put the ClientSSLConfig into a separate file, then use <ClientSSLConfig FromFile='filename'/> in each service, and then you don't need to change everywhere - proposed by Zsombor - but I can't find any example *hrmlgrmpf*...}

%\lstsetCPP
%\lstinputlisting
%	[
%	label=lst:tls_echo_service_cpp,
%	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
%	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
%	]
%{../examples/src/services/tlsechoservice/tlsechoservice.cpp}
%
% Lassen wir mal weg....
%
%
% \lstsetKSH
% \begin{lstlisting}[
% label=lst:tls_echo_arched_invoke,float=htb,
% caption={[Transformation in eine uniforme konzentrische Verteilung.]
%          \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
% $ rm -f /var/log/arched.log
% $ arched -c arched_echoservice.xml  && echo jo ||echo n
% $ tail -n100 -f /var/log/arched.log
% $ killall arched
% \end{lstlisting}
% 
%        ...das auch.....

@@

In this section a new way to implement the client will be introduced. As already mentioned in section~\ref{sec:timeservice_client}, the protocol stack of the client is built up in almost the same way as the one of the service. Indeed, the class~\textit{ClientSOAP} composes the stack with the same MCCs used for the service. Once this is known, it is self-evident to create the client in a simlar manner like the service with an own configuration file.
Listing~\ref{lst:tls_echo_client_cpp} shows the source code of the client program. The main difference to the simple Echo Client presented in the previous chapter is that now the information about the client protocol stack is encapsulated within a configuration file.\\
\lstsetCPP
\lstinputlisting
	[
	label=lst:tls_echo_client_cpp,
	caption={[Client programm which is capable to load a configuration file]
	\textbf{Client programm which is capable to load a configuration file}}
	]
{../examples/src/clients/tlsechoclient/tlsechoclient.cpp}
